Fitting metabolic models to dissolved oxygen data: The Estuarine BAyesian Single-station Estimation method

### 2023-10-13 manu-draft.qmd
need equatags for flextable equations, use flextable 0.9.1 for table caption workaround

![The default prior distributions for $a$, $R$, and $b$ used in EBASE. All priors are normal distributions and truncated to positive values. $b$ is also truncated to a maximum of 0.502 $\left(\text{cm}/\text{hr}\right)/\left(\text{m}^2/\text{s}^2\right)$.](figs/priorplot.png){#fig-priorplot fig-align="center"}

>>>>

![The default prior distributions for $a$, $R$, and $b$ used in EBASE. All priors are normal distributions and truncated to positive values. $b$ is also truncated to a maximum of 0.502 $\left(\text{cm}/\text{hr}\right)/\left(\text{m}^2/\text{s}^2\right)$. Probabilities have been normalized to the maximum probability.](figs/priorplot.png){#fig-priorplot fig-align="center"}
